Re-examining cross-cultural similarity judgements using lexical co-occurrence

### 2023-01-19 code/4_paper/manuscript/manuscript.Rmd
updated manuscript to add ICC

```{r setup, include = FALSE, cache=F}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("irr")

@@

# Appendix
## 1. ICC of item variability and participant variability 
```{r item variability, include = F}
df.icc_item_full <- df_main_analysis %>% 
  select(subject, triad, responses_theme) %>%
  pivot_wider(names_from = subject, values_from = responses_theme)

@@

icc_item_US <- icc(df.icc_item_US, model = "twoway", type = "consistency", unit = "single")$value

>>>>

```{r setup, include = FALSE, cache=F}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("irr")
require(agreement)

@@

# Appendix
## 1. ICC of item variability and participant variability

```{r}
US_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "US"),
                             model = "2A",
                             type = "agreement",
                             unit = "average",
                             object = triad,
                             rater = subject,
                             score = responses_theme,
                             bootstrap = 0)

CN_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "China"),
                             model = "2A",
                             type = "agreement",
                             unit = "average",
                             object = triad,
                             rater = subject,
                             score = responses_theme,
                             bootstrap = 0)

VN_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "Vietnam"),
                             model = "2A",
                             type = "agreement",
                             unit = "average",
                             object = triad,
                             rater = subject,
                             score = responses_theme,
                             bootstrap = 0)

iccs <- tibble(Sample = c("US","China", "Vietnam"),
               `Intra-rater ICC` = c(US_agr$Intra_ICC,
                                     CN_agr$Intra_ICC,
                                     VN_agr$Intra_ICC),
               `Inter-rater ICC` = c(US_agr$Inter_ICC,
                                     CN_agr$Inter_ICC,
                                     VN_agr$Inter_ICC))
```

```{r item variability, include = F}
df.icc_item_full <- df_main_analysis %>% 
  select(subject, triad, responses_theme) %>%
  pivot_wider(names_from = subject, values_from = responses_theme)

@@

icc_item_US <- icc(df.icc_item_US, model = "twoway", type = "agreement", unit = "average")$value
